---
title: "2021 ASA RBC - Session 2 Agenda"
output: html_document
---

# 1) Setup  

```{r Setup, warning=F}
# Loading packages (everytime you open R)
library(dplyr) # wrangling
library(tidyr) # wrangling
library(ggplot2) # plotting
library(readxl) # to read excel files
library(janitor) # to clean data
library(readr) # to export csv

```


```{r Reading data}
soyk

# Checking first rows

# View

```

This study was conducted at four different locations in one year to assess the effect of potassium (K) fertilizer rates on soybean trifoliate K concentration at R4.  

Each study was a randomized complete block design (RCBD) with K rate as the only treatment factor with levels 0, 50, 100, and 150 lbs K20/ac.

```{r Glimpse}

```

```{r Summary}

```

# 2) Data wrangling  
```{r soyk_1 - clean_names()}


```


```{r soyk_2 - filter()}


```

```{r soyk_3 - mutate()}
# Transforming K rate from lbs/ac to kg/ha
0.453592/0.404686
```

```{r soyk_4 - case_when()}


```

```{r soyk_5 - pivot_longer()}

```

```{r soyk_6 - separate()}

```

```{r soyk_7 - select()}

```

```{r soyk_8 - arrange()}

```

```{r soyk_9 and 10 - group_by and summarise}
# group_by


# summarise

```

```{r Piping it all together}



```

```{r Checking if same as without pipe}
# Same result?

```

```{r Saving to file for further analysis}

```

# 3) Exercise  
Starting from soyk, use data wrangling functions in a pipe workflow to generate the average k_pct for each K rate (in kg/ha) within each location (basically, averaging over reps).

Tip: the final data frame will have 16 rows.




