---
title: "2021 ASA RBC - Session 5 Agenda"
output: html_notebook
---

# 1) Setup  
```{r Setup, warning=F}
# Loading packages (everytime you open R)
library(dplyr) # wrangling
library(tidyr) # wrangling
library(purrr) # for iteration
library(ggplot2) # plotting
library(readr) # to read dand write data
library(lme4) # for mixed models
library(car) # Anova
library(broom.mixed) # model diagnostics
library(emmeans) # Anova means
library(multcomp) # pairwise comparisons
library(multcompView) # pairwise comparisons
library(ggthemes) # ggplot customization

```


```{r soyk_w - Reading data}
soyk_w <- read_csv("SoybeanWorkshopProcessed.csv")

# Checking first rows
soyk_w

```

# 2) Exploratory Plots 
```{r Point and curve}


```

# 3) Regression for one Location  
```{r soyk_w2 - Wrangling a bit more}
# Creating Krate as categorical (factor)
soyk_w2 <- soyk_w %>%
  mutate(fk_rate_kgha=factor(k_rate_kgha),
         frep=factor(rep),
         location=factor(location)) 

soyk_w2
```

```{r Extracting only one location}
# Extracting only one location (s1)
soyk_w2_s1 

```

- ANOVA vs. Regression 
- Fixed vs. Random effect

```{r RCBD model for location s1}
options(contrasts = c("contr.sum", "contr.poly"))


```

```{r summary }

```

```{r Anova}

```

# 4) Model Assumptions  
Why is this important?  
Draw example on board showing a bad model for the data.  

```{r Extracting residuals information}
soyk_reg_aug_s1 <- augment(soyk_reg_s1)

soyk_reg_aug_s1$.stdresid <- resid()

```


## 4.1) Within-group errors are iid ~ N(0, var2)  

On this plot, looking for:  
- Spread around zero  
- Homogeneity (no patterns)  
- Outliers (>3 or <-3)  

```{r Standardized Residuals vs. Fitted, message=F, warning=F}
ggplot(soyk_reg_aug_s1, aes(x = .fitted, y = .stdresid))+
  geom_point(aes(color = frep))+
  geom_hline(yintercept = c(-3,0,3), color = "orange")+
  geom_smooth()

```

On this plot, looking for normality (points on top of line)
```{r Quantile-Quantile}
ggplot(soyk_reg_aug_s1, aes(sample = .stdresid))+
  stat_qq()+
  stat_qq_line()
```


## 4.2) Random effects are iid ~ N(0,var1)  

On this plot, looking for normality.  
```{r QQ plot for fRep random effects}
randeff_rep_s1 <- ranef(soyk_reg_s1)[[1]]

ggplot(randeff_rep_s1, aes(sample=`(Intercept)`))+
  stat_qq()+
  stat_qq_line()

```

# 5) Automating analysis for all Locations with group_by(), nest(), and map()  
```{r Automated regression for all locations }

soyk_reg_all
```

```{r Checking ANOVAs}

```

```{r Checking Residuals, message=F, warning=F}

```

# 6) Plotting it all  
```{r Plotting all with regression lines}

```




