---
title: "2021 ASA RBC - Session 3-4 Agenda"
output: html_document
---

# 1) Setup  

```{r Setup, warning=F}
# Loading packages (everytime you open R)
library(dplyr) # wrangling
library(tidyr) # wrangling
library(ggplot2) # plotting
library(readr) # to read files
library(lme4) # for mixed models
library(car) # Anova
library(broom.mixed) # model diagnostics
library(emmeans) # Anova means
library(multcomp) # pairwise comparisons
library(multcompView) # pairwise comparisons
library(ggthemes) # ggplot customization

```

```{r Reading data}
soyk_w

# Checking first rows
soyk_w

```

# 2) Exploratory Plots  
```{r Boxplot }

```

```{r Boxplot by k_rate_kgha}

```

```{r Boxplot by k_rate_kgha by location}

```

```{r Boxplot by k_rate_kgha by location faceted}

```

# 3) ANOVA  
```{r soyk_w2 - Wrangling a bit more}
# Creating Krate as categorical (factor), transforming other columns to factor


```

```{r soyk_mod - RCBD model}
# Changing type of matrix restriction
options(contrasts = c("contr.sum", "contr.poly"))

# Running model


```

```{r Anova}

```

# 4) Model Assumptions  
```{r Extracting residuals information}
# Augmenting

# Adding Pearson's standardized residual


```

## 4.1) Within-group errors are iid ~ N(0, var2)  

On this plot, looking for:  
- Spread around zero  
- Homogeneity (no patterns)  
- Outliers (>3 or <-3)  

```{r Standardized Residuals vs. Fitted, message=F}


```

On this plot, looking for normality (points on top of line).  
```{r Quantile-Quantile}


```


## 4.2) Random effects are iid ~ N(0,var1)  

On this plot, looking for normality.  
```{r QQ plot for Location:fRep random effects}

```

```{r QQ Plot for Location random effects}

```

# 5) Extracting model means and pairwise comparisons 
```{r Expected marginal means for K rates within location}


```

```{r Pairwise comparisons}

```

# 6) Plotting all!  
```{r Boxplot means}

```

```{r Boxplot means, different location ordering}

```

# 7) Exercise  
Customize one of the plots above!  
- Play around with different theme_ options.  
- Play around with different scale_fill_ options.  
- On the x axis title, instead of using / (in K2O/ha), try to find out how to make it superscript.
Tip: you will need to work on the labs() function, and will need to ask on Google.  




