---
title: "2021 ASA RBC - Session 3-4 Agenda"
output: html_document
---

# 1) Setup  

```{r Setup, warning=F}
# Loading packages (everytime you open R)
library(dplyr) # wrangling
library(tidyr) # wrangling
library(ggplot2) # plotting
library(readr) # to read files
library(lme4) # for mixed models
library(car) # Anova
library(broom.mixed) # model diagnostics
library(emmeans) # Anova means
library(multcomp) # pairwise comparisons
library(multcompView) # pairwise comparisons
library(ggthemes) # ggplot customization

```

```{r Reading data}
soyk_w <- read_csv("SoybeanWorkshopProcessed.csv")

# Checking first rows
soyk_w

```

# 2) Exploratory Plots  
```{r Boxplot }
ggplot(soyk_w, aes(x = k_rate_kgha, y = k_pct))+
  geom_boxplot()
```

```{r Boxplot by k_rate_kgha}
ggplot(soyk_w, aes(x = factor(k_rate_kgha), y = k_pct))+
  geom_boxplot()
```

```{r Boxplot by k_rate_kgha by location}
ggplot(soyk_w, aes(x = factor(k_rate_kgha), y = k_pct))+
  geom_boxplot(aes(fill = location))
```

```{r Boxplot by k_rate_kgha by location faceted}
ggplot(soyk_w, aes(x = factor(k_rate_kgha), y = k_pct))+
  geom_boxplot(aes(fill = location))+
  facet_grid(.~location)

```

# 3) ANOVA  
```{r soyk_w2 - Wrangling a bit more}
# Creating Krate as categorical (factor), transforming other columns to factor

soyk_w2 <- soyk_w %>%
  mutate(fk_rate_kgha = factor(k_rate_kgha),
         frep = factor(rep),
         location = factor(location))

soyk_w2
```

```{r soyk_mod - RCBD model}
# Changing type of matrix restriction
options(contrasts = c("contr.sum", "contr.poly"))

# Running model
soyk_mod <- lmer(k_pct ~ (1|location/frep) +
                  location*fk_rate_kgha,
                data = soyk_w2)

```

```{r Anova}
Anova(soyk_mod, type = 3)
```

# 4) Model Assumptions  
```{r Extracting residuals information}
# Augmenting
soyk_mod_aug <- augment(soyk_mod)

# Adding Pearson's standardized residual
soyk_mod_aug$.stdresid <- resid(soyk_mod, 
                               type = "pearson", 
                               scaled = T)

```

## 4.1) Within-group errors are iid ~ N(0, var2)  

On this plot, looking for:  
- Spread around zero  
- Homogeneity (no patterns)  
- Outliers (>3 or <-3)  

```{r Standardized Residuals vs. Fitted, message=F}
ggplot(soyk_mod_aug, aes(x = .fitted, y = .stdresid))+
  geom_point(aes(color = location))+
  geom_hline(yintercept = c(-3,0,3), 
             color = "orange")+
  geom_smooth()

```

On this plot, looking for normality (points on top of line).  
```{r Quantile-Quantile}
ggplot(soyk_mod_aug, aes(sample = .stdresid))+
  stat_qq()+
  stat_qq_line()
```


## 4.2) Random effects are iid ~ N(0,var1)  

On this plot, looking for normality.  
```{r QQ plot for Location:fRep random effects}
randeff_locrep <- ranef(soyk_mod)[[1]] 

ggplot(randeff_locrep, aes(sample = `(Intercept)`))+
  stat_qq()+
  stat_qq_line()

```

```{r QQ Plot for Location random effects}
randeff_rep <- ranef(soyk_mod)[[2]] 

ggplot(randeff_rep, aes(sample = `(Intercept)`))+
  stat_qq()+
  stat_qq_line()

```

# 5) Extracting model means and pairwise comparisons 
```{r Expected marginal means for K rates within location}
soyk_means_locrate <- emmeans(soyk_mod,
                             ~fk_rate_kgha|location)

soyk_means_locrate
```

```{r Pairwise comparisons}
soyk_pwc_locrate <- cld(soyk_means_locrate, 
                       adjust = "none",
                       Letters = letters,
                       reversed = T)

soyk_pwc_locrate <- as.data.frame(soyk_pwc_locrate)

soyk_pwc_locrate
```

# 6) Plotting all!  

```{r Boxplot means}
ggplot(soyk_w2, aes(x = fk_rate_kgha, y = k_pct))+
  geom_boxplot(aes(fill = location), 
               color = "black", 
               alpha = .8)+  
  facet_wrap(~location, 
             scales = "free")+
  scale_y_continuous(limits = c(.5,4))+
  geom_text(data=soyk_pwc_locrate, 
            aes(label = .group, y = emmean), 
            nudge_y = .7, 
            show.legend = F)+
  labs(x = "K Rate (kg K2O/ha)", y = "Plant K (%)")+
  theme_bw()+
  scale_fill_tableau()+
  theme(legend.position = "none")

ggsave(filename="../output/BarMeans.png", 
       width = 5, 
       height = 4)

```

```{r Boxplot means, different location ordering}
levels(soyk_w2$location)

soyk_w2 %>%
  mutate(location = factor(location,
                           levels = c("a1", "s1",
                                      "o2", "w1"))) %>%
  ggplot(aes(x = fk_rate_kgha, y = k_pct))+
  geom_boxplot(aes(fill = location), 
               color = "black", 
               alpha = .8)+  
  facet_wrap(~location, 
             scales = "free")+
  geom_text(data=soyk_pwc_locrate, 
            aes(label = .group, y = emmean), 
            nudge_y = .5, 
            show.legend = F)+
  labs(x = "K Rate (kg K2O/ha)", y = "Plant K (%)")+
  theme_bw()+
  scale_fill_tableau()+
  theme(legend.position = "none")
```

# 7) Exercise  
Customize one of the plots above!  
- Play around with different theme_ options.  
- Play around with different scale_fill_ options.  
- On the x axis title, instead of using / (in K2O/ha), try to find out how to make it superscript.
Tip: you will need to work on the labs() function, and will need to ask on Google.  




