---
title: "2021 ASA RBC - Session 5 Agenda"
output: html_notebook
---

# 1) Setup  
```{r Setup, warning=F}
# Loading packages (everytime you open R)
library(dplyr) # wrangling
library(tidyr) # wrangling
library(purrr) # for iteration
library(ggplot2) # plotting
library(readr) # to read dand write data
library(lme4) # for mixed models
library(car) # Anova
library(broom.mixed) # model diagnostics
library(emmeans) # Anova means
library(multcomp) # pairwise comparisons
library(multcompView) # pairwise comparisons
library(ggthemes) # ggplot customization

```


```{r soyk_w - Reading data}
soyk_w <- read_csv("SoybeanWorkshopProcessed.csv")

# Checking first rows
soyk_w

```

# 2) Exploratory Plots 
```{r Point and curve}
ggplot(soyk_w, aes(x=k_rate_kgha, y=k_pct))+
  geom_point(aes(color=location))+
  geom_smooth(method="lm")+
  facet_grid(.~location)

```

# 3) Regression for one Location  
```{r soyk_w2 - Wrangling a bit more}
# Creating Krate as categorical (factor)
soyk_w2 <- soyk_w %>%
  mutate(fk_rate_kgha=factor(k_rate_kgha),
         frep=factor(rep),
         location=factor(location)) 

soyk_w2
```

```{r Extracting only one location}
# Extracting only one location (s1)
soyk_w2_s1 <- soyk_w2 %>%
  filter(location=="s1")

soyk_w2_s1

```

- ANOVA vs. Regression 
- Fixed vs. Random effect

```{r RCBD model for location s1}
options(contrasts = c("contr.sum", "contr.poly"))

soyk_reg_s1<- lmer(k_pct ~ (1|frep) +
                     k_rate_kgha,
                   data=soyk_w2_s1)

```

```{r summary }
summary(soyk_reg_s1)
```

```{r Anova}
Anova(soyk_reg_s1, type = 3)
```

# 4) Model Assumptions  
Why is this important?  
Draw example on board showing a bad model for the data.  

```{r Extracting residuals information}
soyk_reg_aug_s1 <- augment(soyk_reg_s1)

soyk_reg_aug_s1$.stdresid <- resid(soyk_reg_s1, 
                                   type = "pearson", 
                                   scaled = T)

```


## 4.1) Within-group errors are iid ~ N(0, var2)  

On this plot, looking for:  
- Spread around zero  
- Homogeneity (no patterns)  
- Outliers (>3 or <-3)  

```{r Standardized Residuals vs. Fitted, message=F, warning=F}
ggplot(soyk_reg_aug_s1, aes(x=.fitted, y=.stdresid))+
  geom_point(aes(color=frep))+
  geom_hline(yintercept = c(-3,0,3), color="orange")+
  geom_smooth()

```

On this plot, looking for normality (points on top of line)
```{r Quantile-Quantile}
ggplot(soyk_reg_aug_s1, aes(sample = .stdresid))+
  stat_qq()+
  stat_qq_line()
```


## 4.2) Random effects are iid ~ N(0,var1)  

On this plot, looking for normality.  
```{r QQ plot for fRep random effects}
randeff_rep_s1 <- ranef(soyk_reg_s1)[[1]]

ggplot(randeff_rep_s1, aes(sample=`(Intercept)`))+
  stat_qq()+
  stat_qq_line()

```

# 5) Automating analysis for all Locations with group_by(), nest(), and map()  
```{r Automated regression for all locations }

soyk_reg_all <- soyk_w2 %>%
  group_by(location) %>%
  nest() %>%
  # Fitting RCBD model
  mutate(mod = map(data,
                   ~lmer(k_pct ~ 
                           (1|frep) + 
                           k_rate_kgha,
                         data = .x)
  )) %>%
  # Anova 
  mutate(Anova = map(mod,
                     ~Anova(.x, type = 3)
  )) %>%
  # Augmenting (for diagnostics and predictions)
  mutate(aug=map(mod,
                 ~augment(.x)
  )) %>%
  # Adding standardized residuals 
  mutate(augstd=map2(aug,mod,
                     ~mutate(.data = .x, 
                             .stdresid = resid(.y,
                                               type = "pearson",
                                               scaled = T)
                     ))) %>%
  # Checking residuals 
  mutate(diag1=map2(augstd, location,
                    ~ggplot(data=.x, aes(x=.fitted, y=.stdresid))+
                      geom_point(aes(color=frep))+
                      geom_hline(yintercept = c(-3,0,3), 
                                 color = "orange")+
                      geom_smooth()+
                      labs(title = paste0(.y))
  ))

```

```{r Checking ANOVAs}
soyk_reg_all$Anova
```

```{r Checking Residuals, message=F, warning=F}
soyk_reg_all$diag1
```

# 6) Plotting it all  
```{r Plotting all with regression lines}
soyk_reg_all %>%
  unnest(augstd) %>%
  ggplot(aes(x = k_rate_kgha, y = k_pct, color = location))+
  geom_point(aes(shape = location), 
             size = 2, 
             alpha = .6)+
  #facet_wrap(.~Location)+
  geom_line(aes(y = .fixed, linetype = location), 
            size = 1)+
  labs(x = "K Rate (kg K2O/ha)", 
       y = "Plant K (%)")+
  theme_solarized_2()+
  scale_color_tableau()+
  theme(legend.position = "bottom")

ggsave(filename = "../output/Regression.png", 
       width = 5, 
       height = 4)
```




