---
title: "2021 ASA RBC - Session 3-4 Agenda"
output: html_document
---

# 1) Setup  

```{r Setup, warning=F}
# Loading packages (everytime you open R)
library(dplyr) # wrangling
library(tidyr) # wrangling
library(ggplot2) # plotting
library(readr) # to read files
library(lme4) # for mixed models
library(car) # Anova
library(broom.mixed) # model diagnostics
library(emmeans) # Anova means
library(multcomp) # pairwise comparisons
library(multcompView) # pairwise comparisons
library(ggthemes) # ggplot customization

```

```{r Reading data}
soyk_w <- read.csv("../output/processed.csv")

# Checking first rows
soyk_w

```

# 2) Exploratory Plots  
```{r Boxplot }
ggplot(soyk_w, aes(x=k_rate_kgha,
                   y=k_pct))+
  geom_boxplot()
```

```{r Boxplot by k_rate_kgha}
ggplot(soyk_w, aes(x=factor(k_rate_kgha),
                   y=k_pct))+
  geom_boxplot()
```

```{r Boxplot by k_rate_kgha by location}
ggplot(soyk_w, aes(x=factor(k_rate_kgha),
                   y=k_pct
))+
  geom_boxplot(aes(color=location))
```

```{r Boxplot by k_rate_kgha by location faceted}
ggplot(soyk_w, aes(x=factor(k_rate_kgha),
                   y=k_pct
))+
  geom_boxplot(aes(color=location))+
  facet_grid(.~location)
```

# 3) ANOVA  
```{r soyk_w2 - Wrangling a bit more}
# Creating Krate as categorical (factor), transforming other columns to factor

soyk_w2 <- soyk_w %>%
  mutate(fk_rate_kgha=factor(k_rate_kgha),
         frep=factor(rep),
         flocation=factor(location))

soyk_w2

glimpse(soyk_w2)
```

```{r soyk_mod - RCBD model}
# Changing type of matrix restriction
options(contrasts = c("contr.sum", "contr.poly"))

# Running model
soyk_mod <- lmer(k_pct ~ (1|flocation/frep) + 
                   flocation*fk_rate_kgha,
                 data = soyk_w2 
)


```

```{r Anova}
Anova(soyk_mod, type = 3)
```

# 4) Model Assumptions  
```{r Extracting residuals information}
# Augmenting
soyk_mod_aug <- augment(soyk_mod)

# Adding Pearson's standardized residual
soyk_mod_aug$.stdresid <- resid(soyk_mod,
                                type = "pearson",
                                scaled = T)

```

## 4.1) Within-group errors are iid ~ N(0, var2)  

On this plot, looking for:  
- Spread around zero  
- Homogeneity (no patterns)  
- Outliers (>3 or <-3)  

```{r Standardized Residuals vs. Fitted, message=F}
ggplot(soyk_mod_aug, aes(x= .fitted,
                         y=.stdresid))+
  geom_point()+
  geom_hline(yintercept = c(-3,0,3))+
  geom_smooth()

```

On this plot, looking for normality (points on top of line).  
```{r Quantile-Quantile}
ggplot(soyk_mod_aug, aes(sample = .stdresid))+
  stat_qq()+
  stat_qq_line()

```


## 4.2) Random effects are iid ~ N(0,var1)  

On this plot, looking for normality.  
```{r QQ plot for Location:fRep random effects}
randeff_locrep <- ranef(soyk_mod)[[1]]

ggplot(randeff_locrep, aes(sample = `(Intercept)` ))+
  stat_qq()+
  stat_qq_line()
```

```{r QQ Plot for Location random effects}
randeff_loc <- ranef(soyk_mod)[[2]]

ggplot(randeff_loc, aes(sample = `(Intercept)` ))+
  stat_qq()+
  stat_qq_line()
```

# 5) Extracting model means and pairwise comparisons 
```{r Expected marginal means for K rates within location}
soyk_means_locrate <- emmeans(soyk_mod,
                      ~fk_rate_kgha|flocation)
soyk_means_locrate
```

```{r Pairwise comparisons}
soyk_pwc_locrate <- cld(soyk_means_locrate,
                        adjust="none",
                        reversed = T,
                        Letters = letters
                        ) %>%
  as.data.frame()

soyk_pwc_locrate
```

# 6) Plotting all!  
```{r Boxplot means}
soyk_w2 %>%
ggplot(aes(x=fk_rate_kgha,
                    y=k_pct))+
  geom_boxplot(aes(fill=flocation), 
               alpha=.7,
               show.legend = F)+
  scale_y_continuous(breaks = seq(.5,5,.2))+
  geom_label(data=soyk_pwc_locrate,
            aes(y=emmean,
                label=trimws(.group)),
            label.padding = unit(0.08, "lines")
            )+
  facet_wrap(~flocation,
             scales = "free",
             nrow=1)+
  labs(x=expression("K rate (kg"~ha^-1* ")"),
       y="Trifoliate K (%)")+
  theme_bw()+
  scale_fill_colorblind()

ggsave(filename = "../output/pubready.png", height = 4,
       width = 4
       )

```

```{r Boxplot means, different location ordering}

```

# 7) Exercise  
Customize one of the plots above!  
- Play around with different theme_ options.  
- Play around with different scale_fill_ options.  
- On the x axis title, instead of using / (in K2O/ha), try to find out how to make it superscript.
Tip: you will need to work on the labs() function, and will need to ask on Google.  




