---
title: "2021 ASA RBC - Session 2 Agenda"
output: html_document
---

# 1) Setup 

```{r Setup, warning=F}
# Loading packages (everytime you open R)
library(dplyr) # wrangling
library(tidyr) # wrangling
library(ggplot2) # plotting
library(readxl) # to read excel files
library(janitor) # to clean data
library(readr) # to export csv

```


```{r Reading data}
soyk <- read_excel("../data/SoybeanWorkshop.xlsx")

# Checking first rows
soyk

# View
View(soyk)
```

This study was conducted at four different locations in one year to assess the effect of potassium (K) fertilizer rates on soybean trifoliate K concentration at R4.  

Each study was a randomized complete block design (RCBD) with K rate as the only treatment factor with levels 0, 50, 100, and 150 lbs K20/ac.

```{r Glimpse}
glimpse(soyk)
```

```{r Summary}
summary(soyk)
```

# 2) Data wrangling  
```{r soyk_1 - clean_names()}
soyk_1 <- clean_names(soyk)

soyk_1
```


```{r soyk_2 - filter()}
soyk_2 <- filter(soyk_1, 
                 k_rate_lbac == 0)

soyk_2
```

```{r soyk_3 - mutate()}
# Transforming K rate from lbs/ac to kg/ha
soyk_3 <- mutate(soyk_1,
                 k_rate_kgha=k_rate_lbac*0.453592/0.404686,
                 k_rate_kgha=round(k_rate_kgha,digits = 0))


soyk_3
```

```{r soyk_4 - case_when()}
soyk_4 <- mutate(soyk_3,
                 rep=case_when(
                   plot > 100 & plot < 200 ~ 1,
                   plot > 200 & plot < 300 ~ 2,
                   plot > 300 & plot < 400 ~ 3,
                   plot > 400 ~ 4
                 ))

soyk_4

View(soyk_4)
```

```{r soyk_5 - pivot_longer()}
soyk_5 <- pivot_longer(soyk_4,
                       names_to = "location.k",
                       values_to = "k_pct",
                       cols = c("a1_k_pct",
                                "o2_k_pct",
                                "s1_k_pct",
                                "w1_k_pct"))

soyk_5
```

```{r soyk_6 - separate()}
soyk_6 <- separate(soyk_5,
                   location.k,
                   into = c("location",
                            "k",
                            "pct"))

soyk_6
```

```{r soyk_7 - select()}
soyk_7 <- dplyr::select(soyk_6,
                        k_rate_kgha, rep, 
                        location, k_pct)

soyk_7
```

```{r soyk_8 - arrange()}
soyk_8 <- arrange(soyk_7, location)

soyk_8
```

```{r soyk_9 and 10 - group_by and summarise}
# group_by
soyk_9 <- group_by(soyk_8, location) 
soyk_9

# summarise
soyk_10 <- summarise(soyk_9,
                     mean=sd(k_pct))

soyk_10
```

```{r Piping it all together}
soyk_w <- read_excel("../data/SoybeanWorkshop.xlsx") %>%
  clean_names() %>%
  mutate(k_rate_kgha=k_rate_lbac*0.453592/0.404686,
         k_rate_kgha=round(k_rate_kgha,digits = 0)) %>%
  mutate(rep=case_when(
    plot > 100 & plot < 200 ~ 1,
    plot > 200 & plot < 300 ~ 2,
    plot > 300 & plot < 400 ~ 3,
    plot > 400 ~ 4
  )) %>%
  pivot_longer(names_to = "location.k",
               values_to = "k_pct",
               cols = c("a1_k_pct",
                        "o2_k_pct",
                        "s1_k_pct",
                        "w1_k_pct")) %>%
  separate(location.k,
           into = c("location",
                    "k",
                    "pct")) %>%
  dplyr::select(k_rate_kgha, rep, 
                location, k_pct)

soyk_w





```

```{r Checking if same as without pipe}
# Same result?
identical(soyk_w, soyk_7)
```

```{r Saving to file for further analysis}
write_csv(soyk_w, "../output/processed.csv")
```

# 3) Exercise  
Starting from soyk, use data wrangling functions in a pipe workflow to generate the average k_pct for each K rate (in kg/ha) within each location (basically, averaging over reps).

Tip: the final data frame will have 16 rows.




